---
title: "HW 3"
author: "Zheng Li"
date: "5/7/2020"
output: pdf_document
---

QF 104 HW 104 - Zheng Li

#Importing everything I need for the code
```{r echo=TRUE, message=FALSE, warning=FALSE}
library("readxl")
library(fBasics)
library(reshape)
```


Question 1

#Merging the two database

```{r echo=TRUE, message=FALSE, warning=FALSE}
compustat <- read_excel("COMPUSTAT.xlsx")
crsp <- read_excel("CRSP.xlsx")

merged <- merge(compustat, crsp, by = c("fyear","cusip8"))

```

#Report and graph the linear regression model of data "vol"(x) and "at"(y).
```{r echo=TRUE, message=FALSE, warning=FALSE}
x1 <- merged[["vol"]]
y1 <- merged[["at"]]
relation1 <- lm(y1~x1)
print(summary(relation1))
plot(x1,y1,col = "blue",main = "Vol & At Regression",
     abline(relation1),cex = 1.3,pch = 16,xlab = "vol",ylab = "at")

```

Question 2

#Change the merged data set from monthly to yearly by using the aggregate function.
```{r}
yearMerged1 <- aggregate(merged$vol, by=list(merged$fyear, merged$cusip8, merged$at), FUN=sum, na.rm=TRUE)
```

#Then just repeat the steps in question 1 to report and graph the new regression model.
```{r}
x2 <- yearMerged1[["x"]]
y2 <- yearMerged1[["Group.3"]]
relation2 <- lm(y2~x2)
print(summary(relation2))
plot(x2,y2,col = "blue",main = "Vol & At Regression(Yearly By Sum)",
     abline(relation2),cex = 1.3,pch = 16,xlab = "vol",ylab = "at")

```

Question 3

#Repeat what I did in question 2 but change "sum" to "mean" for aggregation.
```{r}
yearMerged2 <- aggregate(merged$vol, by=list(merged$fyear, merged$cusip8, merged$at), FUN=mean, na.rm=TRUE)
x3 <- yearMerged2[["x"]]
y3 <- yearMerged2[["Group.3"]]
relation3 <- lm(y3~x3)
print(summary(relation3))
plot(x3,y3,col = "blue",main = "Vol & At Regression(Yearly By Mean)",
     abline(relation3),cex = 1.3,pch = 16,xlab = "vol",ylab = "at")

```

Question 4

#Tabulate the coefficients from your three regressions.
```{r}
Table <- matrix(c(relation1$coefficients, relation2$coefficients, relation3$coefficients),ncol = 2, byrow = TRUE)
colnames(Table) <- c("Intercept","x")
rownames(Table) <- c("Montly(Question 1)","Yearly By Sum(Question 2)","Yearly By Mean(Question 3)")
print(Table)
```

